---
title: "Annime_Recommendation_dataset"
author: "Meghashree V"
date: "19-08-2021"
output: html_document
---

### To load the data set  
```{r}
data = read.csv('anime.csv')
```

### To Display rows of data set, By default shows 6 rows   
```{r}
head(data)
```

### To show the number of specified rows i.e for n=10, it will display the first 10 rows  
```{r}
head(data, n=10)
```

### To display the last Rows of your data  
```{r}
tail(data)
```

### To view the previously Loaded named object we use ls() command
```{r}
ls()
```

### The type of object can be ascertained using the class() command
```{r}
class(data)
```

```{r}
class(data$MAL_ID)
```
```{r}
data$MAL_ID[1:4]
```

```{r}
class(dimnames(data))
```

### To show a different number of rows using the n = instruction with last record
```{r}
tail(data, n=3)
```

### To get information about an Data frame and particular columns:
```{r}
summary(data)
```

```{r}
summary(data$Popularity)
```

```{r}
mean(data$Popularity)
```

```{r}
median(data$Popularity)
```

### To pick out item from third row and third columns:
```{r}
data[3,3]
```

### to display the values of third row corresponding to columns from one to four:  
```{r}
data[3,1:4]
```

### for displaying all the rows by leaving out the first value and selecting just the first column:
```{r}
data[,1]
```

### specifying rows and displaying values for all columns:
```{r}
data[c(1,3,5,7),]
```

### specifying several rows and using -4 to display all the columns except the fourth:
```{r}
data[c(1,3,5,7),-4]
```

### To use names of the colums to call the particular column:
```{r}
data[c(1,3,5,7),'Studios']
```

### to use [] to get the details of particular row :
```{r}
data[3,4]
```

### to append use $ and then the name of the required column we get the view of that column data:
```{r}
data$Aired
```
### Shows the median absolute deviation:  
```{r}
mad(data$Popularity)
```
```{r}
mode(data$Popularity)
```
```{r}
var(data$Popularity)
```
```{r}
sd(data$Popularity)
```
```{r}
quantile(data$Popularity)
```

### To find 20% quantile:
```{r}
quantile(data$Popularity,0.2)
```

### To find 20%,50% and 80% quantile:
```{r}
quantile(data$Popularity,c(0.2,0.5,0.8))
```

### To Returns five number summary (minimum, lower-hinge, median, upper-hinge, maximum) for the input data.
```{r}
fivenum(data$Popularity)
```

### Basic command that enables the viewing of columns or row is name():
```{r}
names(data)
```

### For displaying the row names:

```{r}
row.names(data)
```

### For displaying the column names:
```{r}
colnames(data)
```

### To display both row names and the column names at the same time we can use the command dimnames()
```{r}
dimnames(data)
```

### Omitting NA items:
```{r}
length(na.omit(data$Favorites))
```
### str() command is useful to see the object structure:

```{r}
str(data)
```

### structure returns the given object with further attributes set:
```{r}
head(structure(data))
```

### can also look at all the named objects you have at once using the ls.str() command:
```{r}
ls.str(data)
```

### can use the pattern = instruction to narrow down your focus

```{r}
ls.str(pattern = 'data')
```

### length() command used to determine the number of items in an object:

```{r}
length(data)
```

### To extract particular coloumn and row values:

```{r}
tdata = attach(data)
tdata
```

### The max() and min() commands display the largest and smallest values in a numeric object
```{r}
max(data$Favorites)

```

```{r}
max(data$Popularity)
```

```{r}
min(data$Popularity)
```

```{r}
min(data$Favorites)
```

```{r}
head(stack(data))
```

### Sorting default is ascending order:
```{r}
head(sort(data$Popularity))
```


### can get an index using the order() command. This uses the same instructions as the sort() command, but tells you the position of each item along the vector:
```{r}
head(order(data$Popularity))
```

### The rank() command gives the rank number like order() in a slightly different manner when the values are same the ranks are shared between them which is not in order()  
```{r}
head(rank(data$Popularity), n=10)
```

### Displaying selected rows & columns  
```{r}
data[3,3]
```

```{r}
data[3, 1:5]
```

### TO convert from Data frame from matrix:
```{r}
head(as.matrix(data))
```

### The cbind() and rbind() commands assemble a matrix/data frames, by columns or rows, from several other object
```{r}
head(rbind(data))
```

```{r}
head(cbind(data))
```

### Simple Cumulative Commands:

```{r}
head(cumsum(data$Popularity))
```

```{r}
head(cummax(data$Ranking))
```
```{r}
head(cummin(data$Popularity))
```

### The cumulative product

```{r}
head(cumprod(data$Popularity))
```

### The table() command enables you to specify which columns of data you want to use to create your contingency table
```{r}
table(data$Ranked)
```


### To check whether the data extracted is data frame or not
```{r}
is.data.frame(data)

```

```{r}
is.table(data)
```
### The class() command can form the basis of a logical test by using the if() command in the following manner:

```{r}
if(class(data) == 'data.frame') TRUE else FALSE
```

### The seq_along() command creates a simple index:
```{r}
seq_along(data)
```

### Create a basic stem and leaf plot using the stem() command
```{r}
stem(data$Popularity)
```

### Now increase the number of bins used by adding a scale = 2 instruction
```{r}
stem(data$Popularity, scale = 2)
```

### Histogram Plotting:  
```{r}
hist(data$Popularity)
```

```{r}
hist(data$Members)
```

```{r}
hist(data$Favorites)
```
```{r}
hist(data$Watching)
```
```{r}
hist(data$Dropped)
```
```{r}
hist(data$Completed)
```

```{r}
hist(data$Popularity, col = 'lightblue', xlab = 'Popularity', ylim = c(0, 0.1), freq = FALSE)
```

### You can also call on the density function directly via the density() command.
```{r}
density(data$Completed)
```

### Using the Density Function to Draw a Graph
```{r}
plot(density(data$Completed))
```

### Adding density lines to the Existing graphs:  
```{r}
hist(data$Completed, freq = F)
lines(density(data$Completed), lty = 2)
lines(density(data$Completed, k = 'rectangular'))
```

### Commands you can use in relation to the normal distribution:

```{r}
#to generate n random numbers from the normal distribution with mean of 0 and standard deviation of 1.
head(rnorm(data$Popularity, mean = 0, sd = 1))
```

```{r}
# for Returning the probability for the quantile q.
head(pnorm(data$Popularity, mean = 0, sd = 1))
```

### By using rnorm() we can create ideal normal distribution using the mean and standard deviation of the data.  
```{r}
data.norm=rnorm(1000,mean(data$Popularity,sd(data$Popularity)))
hist(data.norm, freq = FALSE)
lines(density(data.norm))
```

### Quantile-Quantile Plot: 
It produces a series of points that appers in a straight line for normal distribution. 
```{r}
qqnorm(data$Popularity)# for non-normal distribution
```

```{r}
qqnorm(data.norm)# for normal distribution
```

```{r}
data.norm2=rnorm(1000,mean(data$Popularity,sd(data$Popularity)))
qqnorm(data.norm2)
```

```{r}
qqnorm(data.norm, main = 'QQ plot of data$Popularity', xlab = 'Theoretical', 
ylab = 'Quantiles for data$Popularity')
qqline(data.norm, lwd = 2, lty = 2)
```

### It is possible to plot one distribution against another as a quantile-quantile plot using the qqplot() command.
```{r}
qqplot(data$Popularity, data$Ranked)
```

```{r}
qqplot(data.norm, data.norm2)
```

### Drawing a straight line on the qqplot() can be done using the abline() command. This command uses the properties of a straight line (that is, y = a + bx) to produce a line on an existing plot. The general form of the command is: abline(a = intercept, b = slope).
```{r}
qqp = qqplot(data$Popularity, data$Members)
abline(lm(qqp$y ~ qqp$x))
```

```{r}
#for normalized data
qqp = qqplot(data.norm, data.norm2)
abline(lm(qqp$y ~ qqp$x))
```

### The basic method of applying a t-test is to compare two vectors of numeric data

```{r}
t.test(data$Popularity, data$Members)
```

### Two-sample t-Test with unequal variance:
```{r}
t.test(data$Popularity,data$Members)
```

### Two-sample t-Test with Equal variances:
#### This can override the default and use the classic t-test by adding the var.equal = TRUE instruction, which forces the command to assume that the variance of the two samples is equal.
```{r}
t.test(data$Popularity, data$Members, var.equal = TRUE)
```


### One sample t-Testing:
#### In this version you supply the name of a single vector and the mean to compare it to (this defaults to 0):
```{r}
t.test(data$Popularity, mu = 5)
```
### Using Directional Hypotheses:
#### In this the direction of the hypotheses can be specified.
```{r}
t.test(data$Popularity, mu = 5, alternative = 'greater')
```
### Two-Sample U-Test:
```{r}
wilcox.test(data$Popularity, data$Members)
```
### One-Sample U-Test:
```{r}
wilcox.test(data$Popularity,exact=FALSE)
```

### Correlation and Covariance:
#### The cor() command determines correlation and cov()command determines covariance.
```{r}
#correlation
cor(data$Popularity, data$Members)
```
```{r}
#Determines covariance between x and y . If x is a matrix or data frame, y can be omitted.
x=cov(data$Popularity, data$Members)
x
```
### The cov2cor() command is used to determine the correlation from a matrix of covariance in the following example:
```{r}
v = as.matrix(x)
cov2cor(v)
```
### Significance Testing in Correlation Tests:
```{r}
cor.test(data$Popularity, data$Members)
```
### Chi-squared tests of association can be carried out using the chisq.test() command.
```{r}
chisq.test(data$Popularity)
```
### BoxPlot’s:
```{r}
boxplot(data$Popularity)
```

```{r}
boxplot(data$Members)
```

```{r}
boxplot(data$Favorites)
```

```{r}
boxplot(data$Watching)
```

```{r}
boxplot(data$Completed)
```

```{r}
boxplot(data$Dropped)
```

```{r}
boxplot(data$On.Hold)
```
### Boxplot for multiple items:
```{r}
boxplot(data$Popularity, data$Members)
```

### Customising Boxplots:
```{r}
boxplot(data$Popularity,data$Members,names=c('Popularity','Members'))
title(xlab="Variable",y="Value")
```

### Horizontal Boxplots:
```{r}
boxplot(data$Popularity, horizontal = T)
title(xlab = 'Popularity')
```
```{r}
boxplot(data$Members, horizontal = T)
title(xlab = 'Members')
```

```{r}
boxplot(data$Completed, horizontal = T)
title(xlab = 'Completed')
```

```{r}
boxplot(data$Completed, horizontal = T)
title(xlab = 'Favorites')
```

```{r}
boxplot(data$Completed, horizontal = T)
title(xlab = 'Watched')
```

```{r}
boxplot(data$Completed, horizontal = T)
title(xlab = 'On.Hold')
```

```{r}
boxplot(data$Completed, horizontal = T)
title(xlab = 'Dropped')
```


### scatter plot’s:

```{r}
plot(data$Popularity,data$Members)
```

```{r}
plot(data$Completed,data$Dropped)
```

### Desired columns can be selected for ploating:
```{r}
 pairs(~ Popularity + Members + Completed, data =data)
```
### Line Charts:
```{r}
 with(data[order(data$Popularity),], plot(sort(Popularity), Completed, type = 'l'))
```

```{r}
plot(data$Popularity, type = 'l' )
```
```{r}
plot(data$Popularity, type = 'b')
```

### Pie chartS:
```{r}
pie(data$Popularity, labels = 'Popularity')
```
```{r}
pie(data$Members, labels = 'Members')
```
```{r}
pie(data$Members, labels = 'Completed')
```
```{r}
pie(data$Members, labels = 'Watched')
```
```{r}
pie(data$Members, labels = 'On.Hold')
```
```{r}
pie(data$Members, labels = 'Dropped')
```

###Cleveland Dot Charts:
```{r}
dotchart(data$Popularity)
```
```{r}
dotchart(data$Members)
```
```{r}
dotchart(data$Completed)
```
```{r}
dotchart(data$Watching)
```

```{r}
data.mat=head(as.matrix(data$Completed))
dotchart(head(data$Completed))
```
### Use the t() command to transpose the matrix and produce your dot plot:
```{r}
dotchart(t(data.mat))
```
### Bar charts:
#### The bar chart is suitable for showing data that fall into discrete categories.
```{r}
barplot(data$Popularity)
```
```{r}
barplot(data$Popularity)
title(xlab = 'Channel', ylab = 'Popularity')
box()
```

```{r}
barplot(data$Popularity, names = row.names(data), ylab = 'Count' ,
col = 'tan')
```


### Horizontal Bars:
```{r}
barplot(data.mat, beside = TRUE, horiz = TRUE)
```
### The analysis of variance using the aov() command
```{r}
temp.aov = na.omit(aov(data$Popularity ~ data$Members, data = data))
temp.aov
```

### To see the classic ANOVA table of results, use the summary() command:
```{r}
summary(temp.aov)
```
### Two-Way ANOVA:
#### In a basic one-way ANOVA you have one response variable and one predictor variable, but you may come across a situation in which you have more than one predictor variable, in such cases use two-way ANOVA.
```{r}
data.aov = aov(Popularity ~ Members + Completed, data = data)
summary(data.aov)
```
### creating new testCol/testRow for addition as a new column/row to the df object (using rep() command):
```{r}
testCol = c(rep(data$Popularity - data$Members, length(data)))
head(testCol)
```

### Adding Rows or Columns:
```{r}
test = data.frame(data, testCol)
head(test)
```

```{r}
test = data
test["Test",] = NA
tail(test)
```
### Column Indexes:
```{r}
col(data, as.factor = F)
```
### Extracting two columns from data:
```{r}
x = data[ , 9:10]
head(x)
```

### Use the apply() command to apply a function over all the rows or columns of a data frame (or matrix):
```{r}
#similar to colMean()
apply(data[ , 9:10], 2, mean)
```
```{r}
apply(data[ , 5:10], 2, mean)
```
```{r}
apply(data[ , 9:10], 2, median)
```
```{r}
apply(data[ , 9:10], 2, var)
```
### Using tapply() to Summarize Using a Grouping Variable:
```{r}
tapply(data$Popularity, data$Type, FUN = mean)
```
```{r}
tapply(data$Members, data$Type, FUN = mean)
```
```{r}
tapply(data$Completed, data$Type, FUN = mean)
```
```{r}
tapply(data$On.Hold, data$Type, FUN = mean)
```
```{r}
tapply(data$Watching, data$Type, FUN = mean)
```
```{r}
tapply(data$Dropped, data$Type, FUN = mean)
```
